Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex
equation > constraint

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points. In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The equations are thus indeed linear.\\

			However, this description contains an infinite number of equations, most of which are redundant. While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times. The next section gives a method to reduce the size of the description.

@@

			In the synchronous case, is has been shown that the equations corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\

			Even then, the number of equations to consider is exponential in the number of tasks. While it has been shown that intervals ending after the end of the busy period are also redundant, this value depends on the $C_i$ and is therefore not usable. The following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.

@@

			To summarize, we reduced the description of the C-space from an infinite number of equations to only the 			equations where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job. Note that this is still 			exponential in the number of tasks.

@@

To summarize, we reduced the number of equation from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.

>>>>

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear constraints describing the convex hull of the admissible points. In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of constraints which, taken together, are a necessary and sufficient condition of feasibility. Those are:
			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The constraints are thus indeed linear.\\

			However, this description contains an infinite number of constraints, most of which are redundant. While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times. The next section gives a method to reduce the size of the description.

@@

			In the synchronous case, is has been shown that the constraints corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\

			Even then, the number of constraints to consider is exponential in the number of tasks. While it has been shown that intervals ending after the end of the busy period are also redundant, this value depends on the $C_i$ and is therefore not usable. The following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.

@@

			To summarize, we reduced the description of the C-space from an infinite number of constraints to only the 			constraints where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job. Note that this is still 			exponential in the number of tasks.

@@

To summarize, we reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
